% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = arara
% arara: pdflatex
% arara: biber
% arara: pdflatex: { synctex: yes }

\documentclass{article}

\usepackage{parskip}
\usepackage{hanging}

\usepackage[
	backend=biber,
	refsection=section,
	% Install both of these styles from https://github.com/semprag/biblatex-sp-unified
	bibstyle=biblatex-sp-unified,
	citestyle=sp-authoryear-comp,
	maxcitenames=3,
	maxbibnames=99
]{biblatex}
\addbibresource{../../lingbib-master.bib}

\DeclareSourcemap{
  \maps[datatype=bibtex]{
    \map{
       \step[fieldsource=sortname]
       \step[fieldset=namea, origfieldval, final]
    }
  }
}

\DeclareLabelname{
    \field{namea}
    \field{shortauthor}
    \field{author}
    \field{shorteditor}
    \field{editor}
    \field{translator}
}

\setlength{\bibhang}{15pt}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=black,
	citecolor=black,
	urlcolor=cyan
}

\newcommand*{\Lingbib}{\href{http://lingbib.org/}{Lingbib}}
\newcommand*{\SP}{\emph{Semantics \& Pragmatics}}
\newcommand*{\UnifiedStyleSheet}{\href{http://celxj.org/downloads/UnifiedStyleSheet.pdf}{Unified Stylesheet for Linguistics}}
\newcommand*{\SPUnified}{\href{https://github.com/semprag/biblatex-sp-unified/}{\Package{biblatex-sp-unified}}}

\newcommand*{\Package}[1]{\texttt{#1}}

\title{Testing document for checking conformity to the \UnifiedStyleSheet}
\author{\Lingbib}
\date{Last updated: \today}

\begin{document}

\maketitle

\begin{abstract}
This is a testing document for checking whether entries in the \Lingbib{} database will be formatted in accordance with the guidelines in the \UnifiedStyleSheet{} when printed in a \LaTeX{} document using  \SP' \href{https://github.com/semprag/biblatex-sp-unified/}{\Package{biblatex} implementation of the Unified Stylesheet for Linguistics (\Package{biblatex-sp-unified})}.
\end{abstract}

\section{Journal articles}

\subsection{Exemplars}

\begin{hangparas}{15pt}{1}

Iverson, Gregory K. 1983. Korean /s/. \textit{Journal of Phonetics} 11. 191--200.

Iverson, Gregory K. 1989. On the category supralaryngeal. \textit{Phonology} 6. 285--303.

Johson, Kyle, Mark Baker \& Ian Roberts. 1989. Passive arguments raised. \textit{Linguistic Inquiry} 20. 219--251.

Murray, Robert W. \& Theo Vennemann. 1983. Sound change and syllable structure in Germanic phonology. \textit{Language} 59(3). 514--528.

\end{hangparas}

\subsection{Output of \Lingbib{} database + \SPUnified}

\nocite{chomsky2013:projection}

\printbibliography[
	heading=none
]

\section{Dissertations}

\subsection{Exemplars}

\begin{hangparas}{15pt}{1}

Stewart, Thomas W., Jr. 2000. \textit{Mutation as morphology: Bases, stems, and shapes in Scottish Gaelic}. Columbus, OH: The Ohio State University dissertation.

Yu, Alan C.~L. 2003. \textit{The morphology and phonology of infixation}. Berkeley, CA: University of California dissertation.

\end{hangparas}

\subsection{Output of \Lingbib{} database + \SPUnified}

\nocite{munn1993:coordinate}

\printbibliography[
	heading=none
]

\end{document}